---
title: "Making it a fab five minutes"
subtitle: "Some handy tips and tricks"
author: 
  -   "Deirdre Toher, University of the West of England, Bristol"
  -   "@dtoher@mastodon.ie; twitter: @dtoher"
date: "2023-05-05"
output:
  xaringan::moon_reader:
    css: ["xaringan-themer.css"]
    lib_dir: libs
    nature:
      highlightStyle: style-mono-light
      highlightLines: true
      countIncrementalSlides: false
    self_contained: true
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(xaringanExtra)
library(xaringanthemer)
library(emo)
```

```{r xaringan-tile-view, echo=FALSE}
xaringanExtra::use_tile_view()
```


```{r broadcast, echo=FALSE}
xaringanExtra::use_broadcast()
```

```{r webcam, echo=FALSE}
xaringanExtra::use_webcam(width=250,height=250, margin="0em")
```

```{r xaringan-fit-screen, echo=FALSE}
xaringanExtra::use_fit_screen()
```


```{r setcolour, echo=FALSE, include=FALSE}
style_mono_accent(base_color = "#958CB3",text_font_size = "1.75rem",inverse_link_color="#FFFFFF")

```

```{r xaringan-editable, echo=FALSE}
xaringanExtra::use_editable(expires = 1)
```


```{r xaringan-banner, echo=FALSE}
xaringanExtra::use_banner(
  bottom_left = "https://dtoher.github.io/YSS_talk/",
  exclude = "title-slide"
)
```



# What's the point?

Why do a rapid fire talk?

.pull-left[### My ideas

- cv
- exposure
- feedback
- prizes!

]
--

.pull-right[### Your additional suggestions

.can-edit.key-audienceReasons[
- thing one
- thing two
]]


---

# Setting Yourself Up to Fail

- Too many slides
--

- Too many messages
--

- Too much information

--
  - text
--

  - mathematics
--

  - graphics


---

# Prepare for success

- One key message
--

- Tempt and tease
--

- Advertise rather than explain
--

- Link to details


---

# Preparing for your talk

- Set up autoplay for timings‽
--

- Rehearse those timings
--

- Create short url for your slides
--

  - Put link at start / at foot of each slide
--

  - Publish link in advance!
--

  - Advertise!
 
  

---

# Short talk ≠ Other types of talk


- Redesign from scratch
--

- Focus on key idea

- Possibly in the form of a worked example

--

- Don't:

  -   introduce what you'll say 
  -   recap what you said!

---

# Being Prepared

- format; need to check!
  - html (should be self contained)
  - pdf
  - powerpoint
- send current version of file to the desk day before
- last minute updates easier if online with short html link to site `r ji("grinning face")`

---

# Standing Out (in a good way)

- Find out your chair in advance
  -   Try to talk to them in advance
- Think about accessibility
- Stick to time
- Be available for questions later
- Perhaps end with link to technical paper?
